### 2019-01-18 texs/paper_base.tex
maybe ast data generation worked

\section{Modelings}

% (TODO)LSTM,Seq2seqの説明、その後Attentionについて説明、さらにその後seq2treeについて説明する。
\subsection{LSTM}
LSTM (Long Short-Term Memory) is a unit of Recurrent Neural Network. 
It is first introduced in \cite{first_LSTM}, for overcoming the vanishing gradient problem and exploding gradient problem.
Roughly speaking, LSTM unit recieves two input vectors, 
the one represents the internal state of the LSTM, and the other is the input for the LSTM unit, 
and LSTM emits one output vectors, which represents the next internal state of the LSTM.

@@

LSTM unit is applied for SMT task in \cite{seq2seq}, as the essential unit of the seq2seq (sequence to sequence) model.
SMT is the task which tries to translate one sentense $sx$ written in a language L into the sentense $sy$ written in another a language M.

@@

The purpose of the decoder network is to estimate the distribution $ p(sy_k|sx,[sy_1,\dots,sy_{k-1}]) $.

The training process is carried out as follows. 
First, $sy$ is tokenized and embedded to vector representation $vy_{1} \dots vy_{m}$ in the same way as $sx$.
And from the start vector $y_begin$ and encoded input $ enc_{n} $, first internal state $ dec_{1}$ is calcuated as $ LSTM_{dec}(enc_{n},y_begin) $.
Then, with for all vector $vy_{k}$, $dec_{k+1}$ is calculated as $ LSTM_{dec}(dec_{k},vy_{k}) $.
Each decoder internal state $ dec_{k} $ is passed to the linear layer $ W_dec $ then softmaxed to a probability vector $ py_{k} $.
The probability vector $ py_{k} $ is intended to represent the probability distribution $ p(sy_k|sx,[sy_1,\dots,sy_{k-1}]) $.
% (TODO)このへんで V_eosについて述べないといけない
So the network is trained to reduce the difference between predicted distribution $ py_{k} $ and actual distribution $ p(sy_k|sx,[sy_1,\dots,sy_{k-1}]) $.
In the experiment, we choiced cross-entropy of $ py_{k} $ and $ p(sy_k|sx,[sy_1,\dots,sy_{k-1}]) $ for loss function.

The inference is obteining $ \argmax_{sy} p(sy|sx) = \argmax_{sy} \prod_{k=1}^n p(sy_k|sx,[sy_1,\dots,sy_{k-1}]) $.
Calculating argmax directly is time consuming, so we have to approximate the argmax by calculating $sy = [sy_1, \dots sy_n]$ sequentially.
First, $sy_1$ is calculated as $ \argmax_{sy_1} p(sy_1|sx,[]) $, where distribution $ p(sy_1|sx,[]) $ is approximated by 
$ softmax(W_dec(dec_{1})) = softmax(W_dec(LSTM_{dec}(enc_{n},y_begin))) $. Then, the next

>>>>

\section{Modeling}

% (TODO)LSTM,Seq2seqの説明、その後Attentionについて説明、さらにその後seq2treeについて説明する。
\subsection{LSTM}
%72 words.
LSTM (Long Short-Term Memory) is a unit of Recurrent Neural Network. 
It is first introduced in \cite{first_LSTM}, for overcoming the vanishing gradient problem and exploding gradient problem.
Roughly speaking, LSTM unit recieves two input vectors, 
the one represents the internal state of the LSTM, and the other is the input for the LSTM unit, 
and LSTM emits one output vectors, which represents the next internal state of the LSTM.

@@

% 477 words.
LSTM unit is applied for SMT task in \cite{seq2seq}, as the essential unit of the seq2seq (sequence to sequence) model.
SMT is the task which tries to translate one sentense $sx$ written in one language into the sentense $sy$ written in another language.

@@

The purpose of the decoder network is to estimate the distribution $ p(sy_k|sx,[sy_1,\dots,sy_{k-1}]) $. 
The training process is carried out as follows. 
First, $sy$ is tokenized and embedded to vector representation $vy_{1} \dots vy_{m}$ in the same way as $sx$.
And from the start vector $y_begin$ and encoded input $ enc_{n} $, first internal state $ dec_{1}$ is calcuated as $ LSTM_{dec}(enc_{n},y_begin) $.
Then, with for all vector $vy_{k}$, $dec_{k+1}$ is calculated as $ LSTM_{dec}(dec_{k},vy_{k}) $.
Each decoder internal state $ dec_{k} $ is passed to the linear layer $ W_dec $ then softmaxed to a probability vector $ py_{k} $.
The probability vector $ py_{k} $ is intended to represent the probability distribution $ p(sy_k|sx,[sy_1,\dots,sy_{k-1}]) $.
% (TODO)このへんで V_eosについて述べないといけない
So the network is trained to reduce the difference between predicted distribution $ py_{k} $ and actual distribution $ p(sy_k|sx,[sy_1,\dots,sy_{k-1}]) $.
In the experiment, we choiced cross-entropy of $ py_{k} $ and $ p(sy_k|sx,[sy_1,\dots,sy_{k-1}]) $ for loss function.

The inference is obteining $ \argmax_{sy} p(sy|sx) = \argmax_{sy} \prod_{k=1}^n p(sy_k|sx,[sy_1,\dots,sy_{k-1}]) $.
Calculating argmax directly is time consuming, so we have to approximate the argmax by calculating $sy = [sy_1, \dots sy_m]$ sequentially.
First, $sy_1$ is calculated as $ \argmax_{sy_1} p(sy_1|sx,[]) $, where distribution $ p(sy_1|sx,[]) $ is approximated by 
$ softmax(W_dec(dec_{1})) = softmax(W_dec(LSTM_{dec}(enc_{n},y_begin))) $. 
Then, the next token $sy_2 = \argmax_{sy_1} p(sy_2|sx,[sy_2]) $ is calculated from $ dec_{1} $ and the vector embedding of $sy_1$, and so on.
When the token $sy_{m+1}$ is the EOF token, generating process is stopped and the sequence $ [sy_1, \dots sy_m]$ is returned as the inference result.

% (TODO) このへんで 図を入れる
% (TODO) 理由/気持ち について述べたいですね。

% (TODO) BiLSTMとmulti-layerについてさらっと

\subsection{Attention}
Attention is a extension module of Seq2Seq model to improve the quality of translation.

\subsection{Seq2Tree}
